Approximate Code: A Cost-Effective Erasure Code for Video Applications in Cloud Storage Systems

### 2019-04-15 ApproximateCode.tex
version 3.4

In this article, we propose Approximate Code for multimedia applications, which is an erasure code using an approximation strategy. Approximate Code aims to ensure different reliability of important and minor data by means of erasure coding, thereby reducing storage overhead. It provides complete recovery when fewer disks fail, and ensures approximate recovery (recover most data) in the event of multiple disk failures. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop and Alibaba Cloud systems. 
\textcolor{blue}{The results show that compared with the typical high-reliability erasure code schemes, Approximate Code significantly reduces reduce the storage overhead and provide higher reliability of important data.}

@@

Although multiple replicas can be used to ensure data availability and reliability, this method is too expensive and is only used to save hot data in practice. In contrast, cold data is far more than hot data, and erasure code (EC) schemes are ideal for storing such data. It provides lower storage overhead and write bandwidth than replication with the same fault tolerance. Currently, many cloud storage systems use erasure code to tolerate disk failures and ensure data availability, such as Windows [], Amazon AWS [] or Alibaba Cloud []. Typical erasure codes configuration use three-disk fault tolerant array (3DFTS). However, its overhead is still too high and is excessive because simultaneous damage of triple disks is relatively rare.

The recently proposed approximate storage strategy can significantly reduce the consumption of storage resources and energy. Common methods are to ensure the reliability of important data while storing the minor data on relatively unreliable media or reducing their error correction coding. Multimedia data is a typical application scenario for approximate storage because they can tolerate data corruption compared to other data. For example, video data records at least 20 frames per second, which makes it difficult for a typical user to perceive the loss of several frames. Also, some pixel errors in the image data do not affect the information of the entire picture. However, the direct application of approximate storage in a cloud storage system will result in minor data being unacceptable volatile.

@@

\iffalse
\begin{table}[]
\begin{tabular}{|c|l|}
\hline
Symbols & Description                          \\ \hline\hline
$n$     & the number of chunks in a stripe     \\ \hline
$m$     & the number of parity chunks          \\ \hline
$r$     & the number of sectors in a chunk     \\ \hline
$s$     & the number of columns of $D_I$       \\ \hline
$t$     & the number of rows of $D_I$          \\ \hline
$D_I$   & the zone of important data sectors   \\ \hline
$D_M$   & the zone of minor data sectors       \\ \hline
$Q$     & the zone of important parity sectors \\ \hline
$P$     & the zone of minor parity sectors     \\ \hline
\end{tabular}
\end{table}
\fi

@@

\textcolor{orange}{Here we give some introduction to existing erasure codes
Specifically, we need to illustrate the existing erasure codes for video applications in detail.
Summarize the existing erasure codes in a table (assume Table 1), and illustrate them whether they satisfy the previous requirements in Section II.A}

@@

\textcolor{gray}{
    text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text text }

@@

\begin{table}[ht]
\centering 
\caption{Comparison of fault tolerance and storage overhead between approximate storage, EC and Approximate Code}\label{tab-AS-RS-AP}
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Schemes}  & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Realibilities & Performance \\ \hline\hline
\multirow{2}{*}{EC} & RS & high & high & medium \\ \cline{2-5} 
\multicolumn{1}{|c|}{} & RAID 6 & medium & medium & high \\ \hline
\multicolumn{2}{|c|}{Ap-Storage}& low & very low & high \\ \hline
\multirow{2}{*}{Ap-Code}& Imp & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
 & Minor &  & medium & medium \\ \hline
\end{tabular}
\end{table}

\subsection{Our Motivation}
Based on Table \ref{tab-AS-RS-AP}, either the existing erasure codes or the approximate storage methods cannot meet the requirements of video applications in the cloud storage system due to the following reasons.

@@

\subsubsection{Decoding Process}
Approximate Code decodes important and minor data in different ways. Since the minor data is only encoded in local way, its decoding process is on the contrary.
The important data is encoded in both local and global ways, so all the local and global parity chunks are used to decode it, which can be divided into 3 steps:
\begin{enumerate}
\item Inter-layer check, reconstruct data using global parity chunks until it exceeds fault tolerance.
\item In-layer check, reconstruct data using local parity chunks until it exceeds fault tolerance.
\item Inter-layer check again, reconstruct using the global parity chunks.
\end{enumerate}

\subsection{Recovery Mode}
When the number of nodes lost per layer does not exceed $r$, the Approximate Code completely recovers all data in \emph{full recovery mode}. If the damage is more severe, the Approximate Code enters the \emph{approximate recovery mode}.

@@

\subsection{RS-based Approximate Code}
\subsection{XOR-based Approximate Code}

\subsection{Fault Tolerance}
In this section we give the fault tolerance of important and secondary data in the approximate code.
We first prove the correctness of our decoding process, and then write a program to exhaust all node failures, giving the data recovery capability under any node loss.
Take the approximate code ($3, 2, 2, 1/3$) as an example.

\iffalse
\subsection{Reconstruct Cost}
In this section, we introduce the recovery overhead for several common failure cases of Approximate Code. The reconstruct cost is defined as the 
\subsubsection{Single node failure}
When any one data node fails, the reconstruction cost of minor data is $k$ read and 1 write, while important data has the cost of $h$ read and 1 write. So the total amount of data that needs to be transferred is 
$$ (1-a)*(k+1) + a*(h+1) $$.

@@

For video data encoded by H.264 or similar format, we define I frames as important data, while P frames and B frames as minor data based on the analysis in section \ref{video storage}. In practical, video data is rarely stored in the original form of H.264 streams (``.264'' files), but is usually storaged in an file such as ``.mp4'' files containing information such as audio. We transcode video files into raw video streams and other data, and we define these non-video data as important because they contain information that the video can't provide and only take up a small amount of space. The feasibility of this definition will be confirmed in \ref{evaluation}.

@@

The data distribution scheme is shown in the figure \ref{Data-distribution-v2}. We present $\omega_i$ as the $\omega$ of Data(i), and $\omega_{max} = \omega_2$.
For example, Data 3 is represnted by blue, and its key segment (10\%) and part of minor segment (10\%) are settled in $D_I$.
The main idea of our data distribution method is to guarantee that each GOP has the same proportion of storage in $D_I$ and $D_M$. This method improves flexibility because it is not necessary to maintain a map that marks the location of each GOP, which makes it is easy to add or delete data at any time. Meanwhile, the method is ideal for streaming video data generated in real time by applications such as monitoring.

@@

\begin{table*}[ht]
\centering
\caption{Summary on Various Erasure Codes}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Name & Fault Tolerance & Storage Overhead & Scalibility & Recovery Cost & \begin{tabular}[c]{@{}c@{}}Computational\\ Complexity\end{tabular} \\ \hline \hline
RS($k,m$) Code & any $m$ disks & $m$ disks & high & high & high \\ \hline
MSR($k,m$) Code & any $m$ disks & $m$ disks & medium & low & very high \\ \hline
Raid 6 & 2 & 2 & low & high & low \\ \hline
SD Code($m,s$) & any $m$ disks and $s$ sectors & $m$ disks and $s$ sectors & low & low & medium \\ \hline
\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Important Data)\end{tabular} & any $m+s$ disks & $m$ disks and $s$ sectors & high & high & medium \\ \hline
\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Minor Data)\end{tabular} & any $m$ disks & $m$ disks and $s$ sectors & high & high & high \\ \hline
\end{tabular}
\end{table*}

\begin{table}[htbp]
\begin{tabular}{|c|c|c|c|c|}
\hline
\begin{tabular}[c]{@{}c@{}}Code\\ Config\end{tabular} & \begin{tabular}[c]{@{}c@{}}Storage \\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Imp)\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Minor)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Important \\ Rate\end{tabular} \\ \hline
(6,2,4,1,2) & 1.600 & 3 & 2 & 0.200 \\ \hline
(8,2,6,1,1) & 1.371 & 3 & 2 & 0.143 \\ \hline
(10,2,8,1,1) & 1.270 & 3 & 2 & 0.111 \\ \hline
(11,2,9,1,1) & 1.238 & 3 & 2 & 0.100 \\ \hline
(11,3,7,1,1) & 1.400 & 4 & 3 & 0.127 \\ \hline
(13,3,10,1,2) & 1.327 & 4 & 3 & 0.184 \\ \hline
(8,2,6,1,2) & 1.412 & 3 & 2 & 0.294 \\ \hline
(8,2,4,1,2) & 1.455 & 3 & 2 & 0.455 \\ \hline
(10,2,6,2,2) & 1.364 & 4 & 2 & 0.273 \\ \hline
(11,3,8,2,2) & 1.467 & 5 & 3 & 0.200 \\ \hline
\end{tabular}
\end{table}

>>>>

In this article, we propose Approximate Code for multimedia applications, which is an erasure code using an approximation strategy. Approximate Code aims to ensure different reliability of important and unimportant data by means of erasure coding, thereby reducing storage overhead. It provides complete recovery when fewer disks fail, and ensures approximate recovery (recover most data) in the event of multiple disk failures. To demonstrate the effectiveness of Approximate Code, we conduct several experiments in Hadoop and Alibaba Cloud systems. 
The results show that compared with the typical high-reliability erasure code schemes, Approximate Code significantly reduces reduce the storage overhead and provide high reliability of important data.

@@

Although multiple replicas can be used to ensure data availability and reliability, this method is too expensive and is only used to save hot data in practice. In contrast, the amount of cold data is far more than hot data, and erasure code (EC) schemes are ideal for storing such data. It provides lower storage overhead and write bandwidth than replication with the same fault tolerance. Currently, many cloud storage systems use erasure code to tolerate disk failures and ensure data availability, such as Windows [], Amazon AWS [] or Alibaba Cloud []. Typical erasure codes configuration use three-disk fault tolerant array (3DFTS). However, its overhead is still too high because the simultaneous damage of triple disks is relatively rare.

The recently proposed approximate storage strategy can significantly reduce the consumption of storage resources and energy. Common methods are to ensure the reliability of important data while storing the unimportant data on relatively unreliable media or reducing their error correction coding. Multimedia data is a typical application scenario for approximate storage because they can tolerate data corruption compared to other data. For example, video data records at least 20 frames per second, which makes it difficult for a typical user to perceive the loss of several frames. Also, some pixel errors in the image data do not affect the information of the entire picture. However, the direct application of approximate storage in a cloud storage system will result in the unimportant data being unacceptable volatile.

@@

\iffalse
\begin{table}[]
\begin{tabular}{|c|l|}
\hline
Symbols & Description                          \\ \hline\hline
$n$     & the number of chunks in a stripe     \\ \hline
$m$     & the number of parity chunks          \\ \hline
$r$     & the number of sectors in a chunk     \\ \hline
$s$     & the number of columns of $D_I$       \\ \hline
$t$     & the number of rows of $D_I$          \\ \hline
$D_I$   & the zone of important data sectors   \\ \hline
$D_M$   & the zone of unimportant data sectors       \\ \hline
$Q$     & the zone of important parity sectors \\ \hline
$P$     & the zone of unimportant parity sectors     \\ \hline
\end{tabular}
\end{table}
\fi

@@

@@

Reed Solomon Code (RS code) is a kind of Maximum Distance Separable (MDS) Codes, which have the optimal storage efficiency. The encoding and decoding operations of RS code are based on Galois Field, which leads to a higher computational complexity comparing to XOR-based codes.

However, due to its high scalability, RS code has been widely applied in traditional cloud storage systems. In a RS code which is delegated by RS($k$, $r$), $n = k + r$ denotes the total number
of nodes participating in the erasure coding schema, $k$ stands for the number of data nodes, and $r$ is the number of parity nodes. Generally data is organized and encoded/decoded with the minimum coding unit block. RS($k$, $r$) can tolerate at most $r$ failures at the same time, and single node failure can be recovered from any $k$ survivors. The encoding case of RS code and the failure tolerance processus are shown in Figure 1.

\begin{figure}[ht]
\centering
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[width=0.52\textwidth]{photo/RS1.jpg}
\includegraphics[width=0.4\textwidth]{photo/RS2.jpg}
\end{minipage}
\caption{Encoding process of RS($5$, $3$)}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.3\textwidth]{photo/RS3.jpg}
\caption{Recovery processing of RS($5$, $3$) in the case of 3 random failure}
\end{figure}

\textcolor{red}{In our case, RS code could be applied. As the important data are uniformly-distributed in every node, the data in every node could be considered independent to each other. The principal of video storage divides the data into a small part of important frame and other subordinate frames. If a storage failure occurs in a node that stores largely the important frame, the data recovery may not be complete because the loss of the important frame could lead to a video quality degradation. In this way, this kind of uniformly-distribution would not allow the failure causing the data loss bigger than expected.}

\textcolor{red}{The data distribution assures the independency of nodes, the recovery of data could follow nearly the theoretical case. The recovery processus need the reversible matrix of original matrix. The calculation is shown in Figure 2.}

Another type of erasure code worth mentioning is XOR based codes, which uses purely XOR operations. There are two different approaches to implement XOR codes. One is to use generator matrix\cite{plank2004practical} for encoding/decoding operations, and the other is done by using specific algorithm for each code\cite{huang2008star}. In nowadays cloud storage systems, erasure codes for correcting two or three disk failures are widely used to ensure the reliability, and XOR-based codes show great advantages on encoding/decoding speed when the storage system is recovering from failures. XOR-based codes can be further categorized as XOR-based codes used in RAID-6 and ones to backup triple disk failure.

When it comes to RAID-6, Maximum Distance Separable (MDS) \cite{jin2009p} \cite{cassuto2009cyclic} \cite{blaum1999lowest} \cite{corbett2004row} \cite{blaum1995evenodd} \cite{bloemer1995xor} codes are frequently discussed. There are two types of MDS codes with different properties. One of them is called horizontal MDS codes, but it suffers from high write complexity and unbalanced I/O distribution. Accordingly, the other is called vertical MDS codes which has a common disadvantage of having resource-consuming partial strip write to continuous data.

A novel and efficient XOR-based RAID-6 code, named hybrid code(h-code) \cite{inproceedings}, is introduced a few years ago. This type of codes exploits the benefits of both horizontal and vertical MDS codes, therefore achieving optimization of partial stripe writes for RAID-6 in addition. H code can be applied to any array of (p+1) disks, where p is a prime number. The parities in H-Code are typical row parity and anti-diagonal parity. H-code does not have a specialized anti-diagonal parity strip, while it distributes the anti-diagonal parity elements among all the disks. Its horizontal parity ensures a partial stripe write to continuous data elements in a row share the same row parity chain, which achieves optimal partial stripe write performance. H code can be applied to any array of (p+1) disks, where p is a prime number. The analysis shows that H-Code achieves excellent performance in storage efficiency, encoding/decoding computational complexity and single write complexity.

@@

\begin{table}[ht]
\centering 
\caption{Comparison of fault tolerance and storage overhead between approximate storage, EC and Approximate Code}\label{tab-AS-EC-AP}
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{Schemes}  & \begin{tabular}[c]{@{}c@{}}Storage\\ Overhead\end{tabular} & Realibilities & Performance \\ \hline\hline
\multirow{2}{*}{EC} & RS & high & high & medium \\ \cline{2-5} 
\multicolumn{1}{|c|}{} & RAID 6 & medium & medium & high \\ \hline
\multicolumn{2}{|c|}{Ap-Storage}& low & very low & high \\ \hline
\multirow{2}{*}{Ap-Code}& Imp & \multirow{2}{*}{low} & high & high \\ \cline{2-2} \cline{4-5} 
 & unimportant &  & medium & medium \\ \hline
\end{tabular}
\end{table}

\subsection{Our Motivation}
Based on Table \ref{tab-AS-EC-AP}, either the existing erasure codes or the approximate storage methods cannot meet the requirements of video applications in the cloud storage system due to the following reasons.

@@

\subsubsection{Decoding Process}
Approximate Code decodes important and unimportant data in different ways. Since the unimportant data is only encoded in local way, its decoding process is on the contrary.
The important data is encoded in both local and global ways, so all the local and global parity chunks are used to decode it, which can be divided into 3 steps:
\begin{enumerate}
\item Inter-layer check, reconstruct data using global parity chunks until it exceeds fault tolerance.
\item In-layer check, reconstruct data using local parity chunks until it exceeds fault tolerance.
\item Inter-layer check again, reconstruct using the global parity chunks.
\end{enumerate}

\subsection{Recovery Mode}

@@

\subsection{RS-based Approximate Code}

\subsection{XOR-based Approximate Code}

\subsection{Fault Tolerance}
In this section we give the fault tolerance of important and unimportant data in the Approximate Code.
We first prove the correctness of our decoding process, and then use a program to 
iterate through all the cases of node failures. Finally, we give the data recovery capability of all cases.

For unimportant data, it only has local parity nodes, so its fault tolerance in Approximate Code($k,r,h,a$) is the same as RS($k,r$), which is any $r$ node failures in $k+r$ nodes in each layer.

For important data, We consider the \emph{full recovery mode} and the \emph{approximate recovery mode} separately. When the number of nodes lost per layer does not exceed $r$, the Approximate Code completely recovers all data in \emph{full recovery mode}. If the damage is more severe, the Approximate Code enters the \emph{approximate recovery mode}.

We still take the Approximate Code ($3, 2, 2, 1/3$) as an example, and discuss the fault tolerance of important and mionor data separately.

Important data nodes can tolerate the loss of any 2r+1 data nodes
At the same time tolerate any r+1 node loss. Only in very rare cases, r+2 nodes are damaged in this way, that is, a data node whose local check node and global check node are damaged at the same time.

First consider only the data nodes:
Second, for the case of all nodes:

\iffalse
\subsection{Reconstruct Cost}
In this section, we introduce the recovery overhead for several common failure cases of Approximate Code. The reconstruct cost is defined as the 
\subsubsection{Single node failure}
When any one data node fails, the reconstruction cost of unimportant data is $k$ read and 1 write, while important data has the cost of $h$ read and 1 write. So the total amount of data that needs to be transferred is 
$$ (1-a)*(k+1) + a*(h+1) $$.

@@

For video data encoded by H.264 or similar format, we define I frames as important data, while P frames and B frames as unimportant data based on the analysis in section \ref{video storage}. In practical, video data is rarely stored in the original form of H.264 streams (``.264'' files), but is usually storaged in an file such as ``.mp4'' files containing information such as audio. We transcode video files into raw video streams and other data, and we define these non-video data as important because they contain information that the video can't provide and only take up a small amount of space. The feasibility of this definition will be confirmed in \ref{evaluation}.

@@

The data distribution scheme is shown in the figure \ref{Data-distribution-v2}. We present $\omega_i$ as the $\omega$ of Data(i), and $\omega_{max} = \omega_2$.
For example, Data 3 is represnted by blue, and its key segment (10\%) and part of unimportant segment (10\%) are settled in $D_I$.
The main idea of our data distribution method is to guarantee that each GOP has the same proportion of storage in $D_I$ and $D_M$. This method improves flexibility because it is not necessary to maintain a map that marks the location of each GOP, which makes it is easy to add or delete data at any time. Meanwhile, the method is ideal for streaming video data generated in real time by applications such as monitoring.

@@

\begin{table*}[ht]
\centering
\caption{Summary on Various Erasure Codes}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Name & Fault Tolerance & Storage Overhead & Scalibility & Recovery Cost & \begin{tabular}[c]{@{}c@{}}Computational\\ Complexity\end{tabular} \\ \hline \hline
RS($k,m$) Code & any $m$ disks & $m$ disks & high & high & high \\ \hline
MSR($k,m$) Code & any $m$ disks & $m$ disks & medium & low & very high \\ \hline
Raid 6 & 2 & 2 & low & high & low \\ \hline
SD Code($m,s$) & any $m$ disks and $s$ sectors & $m$ disks and $s$ sectors & low & low & medium \\ \hline
\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (Important Data)\end{tabular} & any $m+s$ disks & $m$ disks and $s$ sectors & high & high & medium \\ \hline
\begin{tabular}[c]{@{}c@{}}Approximate Code($n,m,s,t$)\\ (unimportant Data)\end{tabular} & any $m$ disks & $m$ disks and $s$ sectors & high & high & high \\ \hline
\end{tabular}
\end{table*}

\begin{table}[htbp]
\begin{tabular}{|c|c|c|c|c|}
\hline
\begin{tabular}[c]{@{}c@{}}Code\\ Config\end{tabular} & \begin{tabular}[c]{@{}c@{}}Storage \\ Overhead\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (Imp)\end{tabular} & \begin{tabular}[c]{@{}c@{}}FT\\ (unimportant)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Important \\ Rate\end{tabular} \\ \hline
(6,2,4,1,2) & 1.600 & 3 & 2 & 0.200 \\ \hline
(8,2,6,1,1) & 1.371 & 3 & 2 & 0.143 \\ \hline
(10,2,8,1,1) & 1.270 & 3 & 2 & 0.111 \\ \hline
(11,2,9,1,1) & 1.238 & 3 & 2 & 0.100 \\ \hline
(11,3,7,1,1) & 1.400 & 4 & 3 & 0.127 \\ \hline
(13,3,10,1,2) & 1.327 & 4 & 3 & 0.184 \\ \hline
(8,2,6,1,2) & 1.412 & 3 & 2 & 0.294 \\ \hline
(8,2,4,1,2) & 1.455 & 3 & 2 & 0.455 \\ \hline
(10,2,6,2,2) & 1.364 & 4 & 2 & 0.273 \\ \hline
(11,3,8,2,2) & 1.467 & 5 & 3 & 0.200 \\ \hline
\end{tabular}
\end{table}
